Geospatial - Assignment 3

### 2025-02-12 hw3/hw3_MoritzPeistNoemiLucchiSimonVellin.Rmd
updating .rmd file with part 1

...

@@

# Import SPEI index 
spei_index <- rast("/Users/noemilucchi/Desktop/spei01.nc")

>>>>

Throughout this notebook, we will follow the same approach. We begin with Data Loading, where we import and prepare our necessary datasets. We then move to Data Manipulation, where we process and transform our data into the appropriate format for analysis. Finally, in the Visualization section, we create plots to effectively communicate our findings.

@@

# Import SPEI index 
spei_index <- rast("/hw3/data/spei01.nc")
